Instructions for developing new pages for the MarineOmics webpage

### 2023-02-08 submissions_instructions.Rmd
incoroprated Sam's edits to submissions instructions

You can add Bibtex references to the file RCN_site-Nov05.bib, and then refer to them in your RMarkdown by adding bibliography: RCN_site-Nov05.bib to the header and citing them in the RMarkdown document. Let's say you have a paper you want to cite by LastName et al. 2023 and the paper's ID in your .bib file is 'LastName2023-xy'.

````
We can reference this paper in-text by adding [@LastName2023-xy] to the end of a sentence. This will produce a reference such as the one below for Tripp et al. 2017.
````

RADseq can produce insightful analyses even in the absence of data, if missing values are handled properly [@Tripp2017-cp].

>>>>

You can add Bibtex references to the file RCN_site-Nov05.bib, and then refer to them in your RMarkdown by adding bibliography: RCN_site-Nov05.bib to the header and citing them in the RMarkdown document. Let's say you have a paper you want to cite by LastName et al. 2023 and the paper's ID in your .bib file is 'LastName2023-xy'. We can reference this paper in-text by adding [\@LastName2023-xy] to the end of a sentence. This will produce a reference such as the one below for Tripp et al. 2017.

*syntax in .Rmd **(not in a code chunk)***:
````
RADseq can produce insightful analyses even in the absence of data, if missing values are handled properly [@Tripp2017-cp].
````

*knitted output*: <br>
RADseq can produce insightful analyses even in the absence of data, if missing values are handled properly [@Tripp2017-cp].
